%%This is a very basic article template.
%%There is just one section and two subsections.
\documentclass[a4paper,12pt,oneside]{book}
\usepackage[latin1]{inputenc}
\usepackage[left=1in, right=1in]{geometry}
\usepackage[font=footnotesize, center]{caption}	% Changes font size of figure captions to small
\usepackage{tikz}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{nomencl}
\usepackage{pslatex} % To have Times New Roman font

\setcounter{tocdepth}{2}
\renewcommand{\baselinestretch}{1.5}
\setlength{\headheight}{15pt}
%%\renewcommand{\chaptername}{}
%%\renewcommand{\thechapter}{}
%%\makenomenclature

\begin{document}
\title{Grid Monitoring}
\author{Theofilos Papapanagiotou}
\date{\today}
\maketitle
\frontmatter

\tableofcontents
%%\printnomenclature
\clearpage
\mainmatter
\pagestyle{fancy}

\chapter[Interim Report]{Interim Report}
\section{Introduction}
Develop an interface which allows the customisable aggregation and display and
information on the performance of a computational grid.
\section{Aims and Objectives}
A clear statement of the Aims and Objectives. Remember, aim is a general statement of what
is to be achieved, and objectives are the procedures used to achieve the aim of the project
\section{Literature Review}
This section should provide a more detailed review of the technical field, largely based upon
survey material. This review is a quick preliminary survey, to discover something of the
'shape' of the relevant field of information; in doing this you will identify key abstracts,
journals, books, series of reports, and so on. Key technical issues will be summarised.
\section[Experimental]{Experimental/investigative methods to be adopted}
An outline of the key activities necessary to complete the project, itemising the experimental
methods to be used (in, for example, a design-based project), or the investigative techniques to
be adopted (in the case of, say, a critical survey).
\section[Time plan]{Time-plan (Gantt Chart)}
Strongly related to the key activities identified above.
\begin{center}
%\input {gantt}
\end{center}
\section[Deliverables]{Deliverables or specific outcomes}
A clear statement of the expected outcome(s).
 
\cite{Bonacorsi2004,Byrom,Byroma,gerndt2004performance,Hobson2007,Huang2007,li2005grid,Taylor2006,zanikolas2007importance}


\backmatter

\bibliographystyle{plain}
\bibliography{books}

\end{document}